

\documentclass{article}

\title{\Huge Final Project Ideas}
\author{\large Chi Zhang James Coleman Gibson}
\date{\small \today}

\begin{document}
\maketitle

\section{Schedule Page Generator}
\subsection*{Description}
Rose-Hulman CS professors all make the schedule pages which students find
extremely useful. Unfortunately, not all professors have the coding know-how
to make one of their own. Our project is to make a schedule page website that
allows professors to customize their class schedule page without any coding
experience. This could include the date, resources, topics, links, files, due
dates, and more. As an extra, this could also include a simple API to interface
with Emacs' org-mode and Trello.

\section{Rose Elective Recommendation}
\subsection*{Description}
Particularly as a freshman it can be difficult to come up with ideas for your
elective classes. Many of the classes you know you would enjoy have filled up
and you don't even know if you would enjoy the choices you have. This problem
could be solved with some machine learning and a website which could suggest
electives to you. You could enter in what you have enjoyed, what you haven't,
and out comes your schedule for the quarter.

\section{Rose-Hulman Grading Helper}
\subsection*{Description}
Organization for graders can be tricky when you have multiple sections,
professors, and graders for a class. Getting feedback to students and splitting
the work among graders requires many documents and a fair amount of confusion.
This can be fixed through a website similar to Moodle but with a grader
centered approach. Graders could see exactly who they have to grade, who they
have already graded, and have the key and a rubric all in one place.

\end{document}
